\chapter{List of Experimental Items}\labapp{items}
\section{Similar Reverse Sobel Sequences}
\ex\context{For her lunch break, Mary often goes to a restaurant around the corner whose staff is always friendly. When she returns to work, she is often very happy, due to the excellent food and service. Today, Mary is having a bad day and has to work through her lunch break. One of her colleagues, Paul, ponders whether or not he should substitute for her, so she can go to the restaurant and hopefully come back in a better mood. He discusses this with their manager, who points out that his sacrifice might be useless, if her mood should not improve.}\speaker{Paul}Well, sure, if Mary went to the restaurant and the staff there was in a foul mood and mean to her, she would not come back happy; but if Mary \MakeUppercase{did} go to the restaurant, she would come back happy.\xe
\ex\context{In Japan, a teacher and his well-behaved class visit the zoo. The only rowdy student of his is disappointed that the zoo's panda is asleep and not doing anything. The student asks the teacher whether or not he should bang against the glass and shout at the panda to wake it up. Loath to fruitlessly explain to the student why that would be an uncouth thing to do, he tries to convince the student to give up his idea as a useless endeavour.}\speaker{Teacher}Sure, if you banged against the glass and the rest of the class decided to do the same thing, the panda would wake up; but if you \MakeUppercase{did} bang against the glass, the panda would continue sleeping. So, there's no point in even trying.\xe
\ex\context{Alone in the wilderness, Marc is forced to march through rainy weather. Six hours before dusk, he finds a cave and seeks shelter in it. As the sun sets, Marc is freezing and his only hope for survival is the one remaining match he still has to light a fire. Unfortunately, the match got a bit wet in the rain; he noticed that immediately after he found the cave and let it air out the remainder of the day. Having only one try, John still waits half an hour after dusk for the match to dry, until he can no longer stomach the cold. Just when he is about to strike the match, he ponders whether or not the match would light.}\speaker{Marc}If I struck this match and it was still wet, it would die in here; but if I \MakeUppercase{did} strike this match, it would light and I would survive the night.\xe
\ex\context{Nicole is madly in love with a guy from her class. She planned on asking him out today. Sadly, however, she made a bad joke earlier this week and her crush was deeply offended by its content. If she explained to him that she didn't really mean it, he might be mollified and her hopes not crushed. Luckily, Sarah is a reasonable person and is capable of apologizing for her wrongdoings. Her friend Sarah lays out the situation for her.}\speaker{Sarah}If you apologized to him and asked him out, he would say yes; but if you \MakeUppercase{did} ask him out, he would say no.\xe
\ex\context{Andy's friend Michael plans to go to a cabin in the woods during the semester break. He is not convinced, however, that it will be a fun trip, because he is terrified of storms and he would have no way out if one took place. His trip would be during an average month of the year and Andy thinks that a storm would be possible but not too likely.}\speaker{Andy}If you went to the cabin and a storm came, your trip would be horrible; but if you \MakeUppercase{did} go to the cabin, it would be a pretty good trip.\xe

\section{Dissimilar Reverse Sobel Sequences}
\ex\context{For her lunch break, Mary often goes to a restaurant around the corner, whose service varies wildy from day to day. On their good days, when she returns to work, she is usually very happy, due to the excellent food and service. Today, Mary is having a bad day and has to work through her lunch break. One of her colleagues, Paul, ponders whether or not he should substitute for her, so she can go to the restaurant and hopefully come back in a better mood. He discusses this with their manager, who points out that his sacrifice might be useless, if her mood should not improve.}\speaker{Paul}Well, sure, if Mary went to the restaurant and the staff there was in a foul mood and mean to her, she would not come back happy; but if Mary \MakeUppercase{did} go to the restaurant, she would come back happy.\xe
\ex\context{In Texas, a teacher and his rowdy class visit the zoo. One of his students is disappointed that the zoo's panda is asleep and not doing anything. The student asks the teacher whether or not he should bang against the glass and shout at the panda to wake it up. Loath to fruitlessly explain to the student why that would be an uncouth thing to do, he tries to convince the student to give up his idea as a useless endeavour.}\speaker{Teacher}Sure, if you banged against the glass and the rest of the class decided to do the same thing, the panda would wake up; but if you \MakeUppercase{did} bang against the glass, the panda would continue sleeping. So, there's no point in even trying.\xe
\ex\context{Alone in the wilderness, Marc is forced to march through rainy weather.\linebreak Shortly before dusk, he finds a cave and seeks shelter in it. As the sun sets, Marc is freezing and his only hope for survival is the one remaining match he still has to light a fire. Unfortunately, the match got a bit wet in the rain. Having only one try, John waits half an hour for the match to dry, until he can no longer stomach the cold. Just when he is about to strike the match, he ponders whether or not the match would light.}\speaker{Marc}If I struck this match and it was still wet, I would die in here; but if I \MakeUppercase{did} strike this match, it would light and I would survive the night.\xe
\ex\context{Nicole is madly in love with a guy from her class. She planned on asking him out today. Sadly, however, she made a bad joke earlier this week and her crush was deeply offended by its content. If she explained to him that she didn't really mean it, he might be mollified and her hopes not crushed. Sadly, Nicole is very headstrong and proud, and she rarerly if ever apologizes for the things she does. Even her friend Sarah thinks it unlikely that she would so so, even though it would get her the desired result. Her friend Sarah lays out the situation for her.}\speaker{Sarah}If you apologized to him and asked him out, he would say yes; but if you \MakeUppercase{did} ask him out, he would say no.\xe
\ex\context{Andy's friend Michael plans to go to a cabin in the woods during the semester break. He is not convinced, however, that it will be a fun trip, because he is terrified of storms and he would have no way out if one took place. His trip would be during the driest month of the year and Andy thinks that a storm would be impossible or at the very least extremely unlikely.}\speaker{Andy}If you went to the cabin and a storm came, your trip would be horrible; but if you \MakeUppercase{did} go to the cabin, it would be a pretty good trip.\xe
\section{Disjoint Reverse Sobel Sequences}
\ex\context{Alex and her friend Steve enter a construction site. Steve doesn't wear his helmet, but carries it around in his hand. This annoys Alex, since it's a dangerous site.}\speaker{Alex}If some construction material fell on your head right now and you wore a helmet, you would probably survive the incident; but if some construction material \MakeUppercase{did} fall on your head right now, you would certainly die. So, wear your goddamn helmet.\xe
\ex\context{Michael is driving a car with his daughter Sarah next to him. Whenever they drive in a car, Sarah forgets to fasten her seat belt, and Michael continuously reminds her to do so by explaining what gruesome fates could befall her, if she didn't.}\speaker{Michael}If I had to pull the emergency brake right now and you wore your seat belt, you would be fine; but if I \MakeUppercase{did} have to pull the emergency brake right now, you would crash through the windshield. So be a good girl and fasten your seat belt. Safety first.\xe
\ex\context{Olga has a son. Olga has tried for a long time to get him to learn how to dance, because she thinks that every man should be able to dance. Having learnt that he has a crush on a girl and that there is a school dance in two weeks, she sees an opportunity to get him to learn how to dance.}\speaker{Olga}If your crush asked you to dance and you actually knew how to, you would leave her deeply impressed; but if your crush \MakeUppercase{did} ask you to dance, you would be pretty embarrassed. So, like I always said junior, learn how to dance.\xe
\ex\context{Mary has a fellow student named John. John is notorious for never paying attention, never leaning anything and never understanding anything. The professor has informed him that she would fail him, should he ever not pay attention again. The professor is currently deciding who she should pick to solve an equation on the blackboard that was given as homework. Mary is trying to make it clear to John that he cannot go on like this.}\speaker{Mary}If the professor asked you right now, whether you could solve the problem at the board, and you knew the answer, she would give you another chance. But if the professor \MakeUppercase{did} ask you right now, whether you could solve the answer, she would fail you. You should start to take this seriously; your future career depends on it.\xe
\ex\context{Steven sees Henry eating one of Olga's sandwiches. Olga is extremely hungry and, to the best of Steven's knowledge, that might've been Olga's last sandwich. As such, he starts berating Henry for just eating other people's stuff without asking.}\speaker{Steven}If you ate her last sandwich right now and gave her something else to eat in return, she would forgive you. But if you \MakeUppercase{did} eat her last chips right now, she will hate your guts. So, be more considerate and ask before you take stuff – you might lose friends over it.\xe
